\textbf{\normalsize 3D Multisystemic Finite Element Model of the Chinchilla Inner Ear}

### 2021-06-28 paper.tex
version 7

The cochlea was modeled primarily based on information obtained directly from MRI imaging using the previously described segmentation process. Characteristic ridges on the surface of the bony labyrinth allowed curves to be drawn along the outside of the cochleas spiraling structure. These curves were connected by planes forming a wedge whose superior face represents Reissner’s Membrane, and whose inferior face represents the basilar membrane. This shape was compared with that seen in literature and was confirmed to the have correct structure. \cite{trevino:chinchmodel} \cite{ekdale:chinchanat} \cite{ni:cochmcx}

talk about LENGTH CORRECTION

The rough geometries of the vestibular, cochlear, facial nerves, and proximal brain tissue were inserted into the initial model of the bony labyrinth and smoothed to have consistent surfaces. The attachment point between brain and nerve was left largely unaltered from original data. The model of the temporal bone, received from $\mu$CT imaging, was inserted into the model to further inform nerve and cochlear geometry. The cochlear nerve was refined by enlarging it to completely fill the space within the spiral-shape of the cochlear membranous labyrinth, using Boolean subtraction of the membranous labyrinth to create a mostly uniform boundary. These efforts were compared with the work of Romano, N., Federici, M., Castaldi, A. in 2019 to ensure accuracy in nerve connectivity and path. \cite{romano:nerves}

\subsection{Meshing}
Only the components relevant to the mechanical model were meshed for finite element analysis in this study. This includes the oval window membrane, round window membrane, cupulas, vestibular maculae, basilar membrane, reissner's membrane, utricle, saccule, semicircular canals, and cochlea. The mechanical model was meshed with a total of XX tetrahedral elements and xx nodes using the software Hypermesh. Solid structures used the Solid185 element type while fluids, endolymph and perilymph, were modeled using the Fluid40 element type. A higher number of elements were selected for the basilar membrane in comparison to the rest of the model, XX in total. All components were initially meshed with quadrilateral elements in 2D then split to yield a model with surface represented entirely by triangular elements. Components were assigned their respective thicknesses as seen in TABLE XXX and given proper connectivity using the imprint, extend, and create element tools native to Hypermesh.

@@

\section{Results}
\subsection{Geometry}
A working mechanical model model was constructed with accurate geometries for the bony and membranous labyrinths of the chinchilla inner ear with response evaluable at the basilar membrane, cupulas, and vestibular maculae. This is augmented by models of the vestibulocochlear nerve, auditory cortex, and temporal bone structure for use in later electrical analysis. Features of the mechanical model which differentiate it from others include the presence of the utricle, saccule, vestibular maculae, and geometrically accurate cochlea. A FEW FIGURES OF COMPLETED MECHANICAL MODEL, MAIN FEATURES. Figure \ref{wm} denotes the locations of the round and oval window membranes.

>>>>

The cochlea was modeled primarily based on information obtained directly from MRI imaging using the previously described segmentation process. Characteristic ridges on the surface of the bony labyrinth allowed curves to be drawn along the outside of the cochleas spiraling structure. These curves were connected by planes forming a wedge whose superior face represents Reissner’s Membrane, and whose inferior face represents the basilar membrane. This shape was compared with that seen in literature and was confirmed to the have correct structure. \cite{trevino:chinchmodel} \cite{ekdale:chinchanat} \cite{ni:cochmcx} The cochlea was scaled until the basilar membrane was approximately the average length in chinchillas of 18.3 mm along its midline. (Bohne and Carr, 1979; Hardy, 1938)

The rough geometries of the vestibular, cochlear, facial nerves, and auditory cortex were inserted into the initial model of the bony labyrinth and smoothed to have consistent surfaces. The attachment point between brain and nerve was left largely unaltered from original data. The model of the temporal bone, received from $\mu$CT imaging, was inserted into the model to further inform nerve and cochlear geometry. The cochlear nerve was refined by enlarging it to completely fill the space within the spiral-shape of the cochlear membranous labyrinth, using Boolean subtraction of the membranous labyrinth to create a mostly uniform boundary. These efforts were compared with the work of Romano, N., Federici, M., Castaldi, A. in 2019 to ensure accuracy in nerve connectivity and path. \cite{romano:nerves}

\subsection{Meshing}
Only the components relevant to the mechanical model were meshed for finite element analysis in this study. This includes the oval window membrane, round window membrane, cupulas, vestibular maculae, basilar membrane, reissner's membrane, utricle, saccule, semicircular canals, and cochlea. The mechanical model was meshed with a total of 414,629 tetrahedral elements and 90,696 nodes using the software Hypermesh. Mesh size convergence analysis was not conducted for this model due to the already very fine average element size of about 0.2 mm, more than sufficient in the case of previous models like those seen in (JUNFENG PAPER, GAN PAPER). However, applying mesh size convergence analysis to future iterations of the model may reduce the processing power and time necessary for simulation. Tissues of all kinds were modeled using the Solid185 element type while the fluids, endolymph and perilymph, were modeled using the Fluid40 element type. A fine ruled mesh composed of 8,738 elements was chosen for the basilar membrane. All components were initially meshed with quadrilateral elements in 2D then split to yield a model with surfaces represented entirely by triangular elements. Components were assigned their respective thicknesses as seen in TABLE XXX and given proper connectivity using the imprint, extend, and create element tools native to Hypermesh.

@@

\section{Results}
\subsection{Geometry}
A working mechanical model was constructed from accurate geometries for the bony and membranous labyrinths of the chinchilla inner ear with response evaluable at the basilar membrane, cupulas, and vestibular maculae. This is augmented by .stl models of the vestibulocochlear nerve, auditory cortex, and temporal bone structure for use in later electrical analysis. Features of the mechanical model which differentiate it from others include the presence of the utricle, saccule, vestibular maculae, and geometrically accurate cochlea. A FEW FIGURES OF COMPLETED MECHANICAL MODEL, MAIN FEATURES. Figure \ref{wm} denotes the locations of the round and oval window membranes.
